\documentclass{article}
\usepackage{enumitem}

\title{Reflective Paragraph}
\author{Owen Sowatzke}
\date{December 6, 2023}
	
\begin{document}
	\maketitle

	The project helped me better understand topics from ECE 501B such as orthonormal basis vectors, inner products, eigenvalue decomposition, and singular value decomposition (SVD). Beyond the standard course content, I also learned about principle component analysis (PCA) and how the SVD can be used to implement it. There are existing course resources that discuss PCA and a lecture in which image compression with SVD was briefly discussed. As part of the project, I explained the relationship between these concepts and specifically showed how image compression with SVD was equivalent to performing PCA and discarding less important principle components. I think this relationship may be beneficial to include in the ECE 501B material, specifically in the extra lecture on PCA. Overall, I enjoyed performing research, learning from the selected sources, and implementing the image compression algorithm. One of the few things I did not enjoy was having to explicitly call out relationships between the project material and ECE 501B in the report.
	\begin{itemize}
	
		\item Reflection on what you learned as a result of completing the project
	
		By completing the project, I learned about Principle Component Analysis (PCA) and how it can be performed using a Singular Value Decomposition (SVD).
		 
		\item Brief description of description of division of work
		
		I created functions which perform PCA compression, reconstruct compressed images, and compute the compression ratio. Scott Thoesen created functions which compute the PSNR and generate the report plots.
		
		I wrote the abstract, the principle component analysis section, and image compression using PCA section of the report. Scott wrote the introduction, background main paragraph, singular value decomposition, and compressibility upper bounds sections, the results, and conclusion.
	
		\item How did your project experience help with your understanding of the course material?
	
		The project helped me better understand Singular Value Decomposition, and enhanced my understanding of Eigenvalue Decomposition, orthonormal basis, and inner products. 
		
		\item Do you think the material you selected for your project should be included as part of the normal course material or as additional reading material in ECE 501b?
	
		\item What did you like about the project?
	
		\item What did you not like about the project?
		 
	\end{itemize}
\end{document}
